---
title: "Lab 1"
author: "Lydia English, Earl Hur, Min Zhang"
date: "February 6, 2019"
output: html_document
---

```{r, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(openintro)
library(ggplot2)
library(plotly)
library(maps)
library(tidyr)
#library(maptools)
#library(rgdal)
#library(rgeos)
```

Here is the link to our github [repo](https://github.com/lydiaPenglish/Lab-1)

### Building a Book
**Documenting errors and solution approaches**

1. There were many packages that needed to be installed to knit the index.Rmd. The first problem that we have ran into was that the *emo* package was not available from usual CRAN repository. Another issue came with an error message: *In system(cmd) : 'make' not found* 
  Instead of installing this package from the CRAN, we installed this package through hadley's github. Using *devtools::install_github("hadley/emo")*, we could successfully install the package.

2. Another error we have come across is in the Rcpp.Rmd document:

`Line 77 Error in sourceCpp(code = code, env = env, rebuild = rebuild,` 
`cacheDir = cacheDir, : Error 1 occured building shared library. Calls:` 
`local ... withVisible -> eval -> eval -> cppFunction -> sourceCpp`

If we navigate to line 77 in the Rcpp.Rmd document we find the following script:

```{r add, eval=FALSE}
cppFunction('int add(int x, int y, int z) {
  int sum = x + y + z;
  return sum;
}')
# add works like a regular R function
add
add(1, 2, 3)
```

We've tried downloading and updating Rtools and making sure other packages were updated but this was unsuccessful. However another group member was succesfully able to knit the .html file so this wasn't a problem across all computers. The last word in Chapter 15 was pseudo-class from the group menbers who successfully knit the index.rmd file.

3. The last unsolvable problem occurred in Line 783 in `Conditions.Rmd`. Not sure about the meaning of the error message: `err` inherits from `warning/condition` not `error_bad_argument`. So the chunk of Lines 783-788 was commented out to avoid error message.  

###Weather Stations

**Plotting Weather Stations in the U.S.**

```{r, cache=FALSE, message=FALSE, warning=FALSE}
col_positions <- readr::fwf_widths(
  c(2, 1, 2, 6, 9, 10, 8, 2, 30, 8, 8, 7, 2)
)

weather <- data.frame(readr::read_fwf("ushcn-v2.5-stations.txt", col_positions = col_positions))

names(weather) <- c("Country", "Network", "ID", "COOP", "Latitude", "Longitude", "Elevation", "State", "Name", "Comp1", "Comp2", "Comp3", "DIFF")

weather$DIFF <- as.factor(weather$DIFF)

states_map <- map_data("state") # data for outlines of US states

tzcolor <- c("plum","lightcoral", "khaki", "lightblue") 

weather <- weather %>% 
  mutate(StateFull = tolower(abbr2state(State)))

states_txt <- data.frame(state.center, state.abb)
states_txt <- states_txt[-which(states_txt$state.abb %in% c("AK", "HI")), ]

weather$Timezone <- ifelse(weather$DIFF==5, "Eastern",
                           ifelse(weather$DIFF==6, "Central",
                                  ifelse(weather$DIFF==7, "Mountain", "Pacific")))



p_weather <- ggplot(weather) +
  geom_map(aes(map_id = StateFull, fill = Timezone), size=0.5, color="white", map = states_map) +
  expand_limits(x = states_map$long, y = states_map$lat) +
  geom_point(aes(Longitude, Latitude, colour = Elevation, 
                 text=paste("State: ", toupper(StateFull), 
                            "<br>Longitude: ", Longitude, 
                            "<br>Latitude: ", Latitude, 
                            "<br>Elevation: ", Elevation,
                            "<br>Time Zone: ", Timezone)), cex = 1.5) +
  geom_text(data = states_txt, aes(x = x, y = y, label = state.abb), size = 3, fontface = "bold")+
  labs(x = "Longitude", y = "Latitude", title = "Weather Station") +
  scale_colour_gradientn(colours=c("forestgreen","goldenrod","brown2"))+
  scale_fill_manual(name="", values = tzcolor) +
  theme_light() +
  theme(legend.position="bottom",
        legend.box = "vertical")

ggplotly(p_weather, tooltip = "text") %>% layout(legend=list(orientation = "h", y = -0.2))
```


### More Weather Data

**Downliading gz file and making it available from R.**
```{r, cache=FALSE}
temp <- tempfile()
download.file("ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn.tavg.latest.raw.tar.gz",temp)
untar(temp)
unlink(temp)
```

**Count the number of files.**
```{r, cache=FALSE}
# Count the number of files in the downloaded and extracted folder. 
# (Note that the last number(s) in the folder name will need to be changed depending on the date the folder was downloaded/unzipped)
FileList <- list.files('./ushcn.v2.5.5.20190206')
FileList %>% length()
```

**Name of the file containing Lydia's hometown.**
```{r, cache=FALSE}
weather %>% 
  separate(Name, c('City', 'Other'), sep=" ", extra = "merge", fill = "right")%>% 
  filter(City == "PROVIDENCE", State == "RI") %>% 
  mutate(FileName = paste0(Country, Network, ID, COOP, ".raw.tavg")) %>% 
  pull(FileName)

```

Lydia's hometown is Providence RI, and it corresponds to USH00376698.
